\chapterwithauthor{Anne Gentle}{Documentation and My Former Self}
{文档和以前的我}
\authorbio{Anne Gentle is the fanatical technical writer and community
documentation coordinator at Rackspace for OpenStack, an open source cloud
computing project. Prior to joining OpenStack, Anne worked as a community
publishing consultant, providing strategic direction for professional writers
who want to produce online content with wikis with user-generated pages and
comments. Her enthusiasm for community methods for documentation prompted her to
write a book about using social publishing techniques for technical
documentation titled Conversation and Community: The Social Web for
Documentation. She also volunteers as a documentation maintainer for FLOSS
Manuals, which provides open source documentation for open source projects.}

{
AG 是个疯狂的技术写手和社区文档贡献者，在rackspace公司工作，致力于OpenStack，一个
开源云计算项目。在加入OpenStack之前，Anne是社区的出版顾问，为那些想利用wikis和用户
产生页面、评论专业的作者，提供策略方向。她对文档生成的社区的方法的热情，促使她写了本
关于利用社会出版技术服务于技术文档的书，名为Conversation and Community:The Social
 Web for Documentation。她还作为志愿者，维护FLOSS的手册。FLOSS手册以开源文档的形式
为开源项目服务。
}

\noindent{}An intriguing premise -- spill my guts about what I wish I knew about open
source and documentation. Rather than tell you what I wish you knew about open
source and documentation, I must tell you what I wish my former self knew. The
request evokes a sense of regret or remorse or even horrified notions of ``What
was I thinking?'' 

一个有趣的前提--倾诉关于我希望我知道的关于开源和文档。
而不是告诉你我希望你了解开源和文档的种种。
我必须告诉你，什么是我希望曾经的自己所知道的。
这请求唤起了一种遗憾、悔恨甚至惊骇的概念关于``我当时在想什么？''

In my case, my former self was just five years younger than now, a
thirty-something established professional. In contrast, others may recall their
first experiences with open source as a teenager. Jono Bacon in his book,
\textit{Art of Community}, recounts standing in front of an apartment door with
his heart pounding, about to meet someone he had only talked to online through
an open source community. I have experienced that first in-person meeting with
people I have only met online, but my first serious foray into the world of open
source documentation came when I responded to an emailed request for help. The
email was from a former coworker, asking for documentation help on the XO
laptop, the charter project for One Laptop Per Child. I pondered the perceived
opportunity, talking to my friends and spouse, wondering if it would be a good
chance to experiment with new doc techniques and try something I had never done
before, wiki-based documentation. Since that first experimentation, I have joined
OpenStack, an open source project for cloud computing software, working full
time on community documentation and support efforts. 

对我而言，之前的我不过是比现在年轻了5岁，一个30岁建立了专业东西的人。
相比之下，别人也许回忆他们第一次接触开源时还是个少年。
Jono Bacon在他的书中，\textit{Art of Community}，多次记录激动的
站在公寓门前，即将面对之前只通过开源社区交流过的某人。
我有这样的经历，第一次与只在网上交流过的人开会，但是我第一次正式进军开源
文档的世界，是我回复一封求助邮件的时候。
那封邮件来自之前的合作人，询问文档帮助在XO（指极品）电脑上，那是个授权项目
为一个孩子配一台电脑。我权衡着这个察觉到的机会，同我朋友和丈夫交流，想着是否
它是个很好的机会，去试验新的文档技术，尝试我之前从没做过的，基于wiki的文档。
从那第一次实验后，我就加入了OpenStack，一个开源云计算软件项目，全职投入到
社区文档和协助。

I immediately think of the many contradictions I have found along the way. I
have uncovered surprising points and counterpoints for each observation. For
example, documentation absolutely matters for support, education, adoption, yet,
an open source community will march on despite a lack of documentation or
completely flawed docs. Another seeming juxtaposition of values is that
documentation should be a good onboarding task, a starting point for new
volunteers, yet new community members know so little that they can not possibly
write or even edit effectively, nor are newbies familiar with the various
audiences served by doc. Word on the street lately is that ``developers should
write developer docs'' because they know the audience well and can serve others
like themselves best. In my experience, new, fresh eyes are welcome to the
project and some people are able to write down and share with others those
fresh, empathetic eyes. You do not want to create a ``newbies-only'' culture
around docs, though, because it is important that the key technical community
members support doc efforts with their contributions and encourage others to do
so. 

我立即开始思考很多沿途发现的矛盾。
我没有为每个观察覆盖惊人的观点和对照物。
举个例子，文档对于支持、教育、采用绝对的重要，然而，一个开源社区仍会发展，尽管缺少文
档或完全杂乱的文档。
另一个并列的价值是，文档工作需要被当做一个好的新人培训工作，作为新志愿者的起点，
否则新社区成员知道的太少，以至于他们不能写或者高效的编辑，也不会有新人熟悉多种
被文档服务的观众。最近流行说，``开发者应该写开发者文档''因为他们了解观众，可以把别
人服务的和自己一样好。在我的经验中，新兴的眼光

A bit of a dirty little secret for documentation related to open source projects
is that the lines drawn between official docs and unofficial doc projects are
blurred at best. I wish I had known that documentation efforts get forked all
the time, and new web sites can sprout up where there were none. Sprawling docs
do not offer the most efficient way for people to learn about the project or
software, but a meandering walk through a large set of web documentation might
be more telling to those who want to read between the lines and interpret what
is going on in the community through the documentation. Lots of forking and
multiple audiences served may mean that the product is complex and serves many.
It also can mean that no strong core documentation ethos exists in the
community, so unorchestrated efforts are the norm. 

I wish when I started that I had some ability to gather the ``social weather''
of an online community. When you walk into a restaurant with white tablecloths
and couples dining and a low-level volume of conversations, the visual and
auditory information you receive sets the ambiance and gives you certain clues
about what to expect from your dining experience. You can translate this concept
of social weather to online communities as well. An open source community gives
certain clues in their mailing lists, for example. A list landing page prefixed
with a lot of rules and policy around posting will be heavy in governance. A
mailing list that has multiple posts emphasizing that ``there are no dumb
questions'' is more approachable for new doc writers. I also wish I knew of a
way to not only do a content audit -- a listing of the content available for the
open source project -- but also to do a community audit -- a listing of the
influential members in the open source community, be they contributors or
otherwise.

Lastly, an observation about open source and doc that I have enjoyed validating
is the concept that documentation can occur in ``sprints'' -- in short bursts of
energy with a focused audience and outline and resulting in a known set of
documentation. I was so happy to hear at a talk at SXSW Interactive that sprints
are perfectly acceptable for online collaboration and you could expect lags in
energy level, and that is okay. Software documentation is often fast and furious
in the winding-down-days of a release cycle, and that is acceptable in open
source, community-based documentation. You can be strategic and coordinated and
still offer a high-energy event around documentation. These are exciting times
in open source, and my former self felt it! It is a good thing you can keep
learning and growing your former self into your current self with the collection
of advice to tote along with you.
